Meta-analysis of the `ironic' effects of intergroup contact

### 2020-08-27 manuscript/manuscript.Rmd
run meta-biases and confirmatory moderator analyses

```{r, fig_width = "100%", fig.align = "center", fig.cap = "Results of preregistered analyses. (\\textbf{A}) Posterior distributions for the estimated mean correlation coefficient, highlighting the proportion of posterior samples for which $r_\\text{mean} < 0$. (\\textbf{B}) Posterior predictive distributions  for the estimated study-wise correlation coefficients."}
knitr::include_graphics("../figures/figure-3.pdf") 
```

>>>>

```{r, fig_width = "100%", fig.align = "center", fig.cap = "Results of preregistered analyses. (\\textbf{A}) Posterior distributions for the estimated mean correlation coefficient, highlighting the proportion of posterior samples for which $r_\\text{mean} < 0$. (\\textbf{B}) Posterior predictive distributions for the estimated study-wise correlation coefficients, based on point estimates of the $\\mu$ and $\\tau_J$ parameters, with point estimates for the estimated correlation coefficients for all studies."}
knitr::include_graphics("../figures/figure-3.pdf") 
```

### 2020-08-27 manuscript/manuscript.tex
run meta-biases and confirmatory moderator analyses

\caption{Results of preregistered analyses. (\textbf{A}) Posterior distributions for the estimated mean correlation coefficient, highlighting the proportion of posterior samples for which $r_\text{mean} < 0$. (\textbf{B}) Posterior predictive distributions  for the estimated study-wise correlation coefficients.}\label{fig:unnamed-chunk-3}
\end{figure}

>>>>

\caption{Results of preregistered analyses. (\textbf{A}) Posterior distributions for the estimated mean correlation coefficient, highlighting the proportion of posterior samples for which $r_\text{mean} < 0$. (\textbf{B}) Posterior predictive distributions for the estimated study-wise correlation coefficients, based on point estimates of the $\mu$ and $\tau_J$ parameters, with point estimates for the estimated correlation coefficients for all studies.}\label{fig:unnamed-chunk-3}
\end{figure}
